Response to decision letter

### 2023-05-30 manuscript/manuscript.Rmd
add edits to EJM's edits

Recently, @powell2020quantifying showed in a simulation analysis that secondary calibrations using node dates based on previous molecular clock analyses can be as good as primary calibrations.
Using several secondary calibrations (as opposed to just one) can provide sufficient information to alleviate or even neutralize potential biases [@shaul2002playing; @graur2004reading; @sauquet2013practical]. <!--\textcolor{red}{LLSR: What does our cross validation analysis show in relation to  the effect of using secondary calibrations for a dating analysis that does not make any prior assumptions on the nature of the calibrations themselves? the age difference between primary and secondary calibrations?}--> Our cross validation analysis also provides insight into the application of secondary calibrations. Node ages summarized with DateLife and those from the original studies are well correlated (Supplementary Figs. S2-S20). We also note that DaetLife estimates for nodes closer to the root tend to be slightly younger than ages from the original studies. In contrast, nodes closer to the tips tend to be slightly older when estimated using our secondary calibrations than ages from the original studies. The only exception to this trend was observed in @burns2014phylogenetics chronogram, which generally displays much younger node ages when estimated using secondary calibrations than the original study (Supplementary Figs. S1, S5), supporting previous observations [@sauquet2012testing; @schenk2016sec]. However, these younger dates are likely an example of how multiple secondary calibrations can correct erroneous estimates, as dates on the @burns2014phylogenetics tree were estimated using a secondary calibration based on a previously estimated molecular evolution rate across birds, and were major outliers compared to alternate estimates for the same nodes based on primary fossil calibrations (figure ??).

>>>>

Recently, @powell2020quantifying showed in a simulation study that secondary calibrations using node ages based on previous molecular clock analyses can be as good as primary calibrations.
Using several secondary calibrations (as opposed to just one) can provide sufficient information to alleviate or even neutralize potential biases [@shaul2002playing; @graur2004reading; @sauquet2013practical]. <!--\textcolor{red}{LLSR: What does our cross validation analysis show in relation to  the effect of using secondary calibrations for a dating analysis that does not make any prior assumptions on the nature of the calibrations themselves? the age difference between primary and secondary calibrations?}--> Our cross validation analysis also provides insight into the application of secondary calibrations. Node ages summarized with DateLife and those from the original studies are well correlated (Supplementary Figs. S2-S20). We also note that DateLife estimates for nodes closer to the root tend to be slightly younger than ages from the original studies. In contrast, nodes closer to the tips tend to be slightly older when estimated using our secondary calibrations than ages from the original studies. The only exception to this trend was observed in @burns2014phylogenetics chronogram, which generally displays much younger node ages when estimated using secondary calibrations than the original study (Supplementary Figs. S1, S5), supporting previous observations [@sauquet2012testing; @schenk2016sec]. However, these younger dates are more likely an example of how multiple secondary calibrations can correct erroneous estimates, as dates on the @burns2014phylogenetics tree were obtained using a single secondary calibration based on a previously estimated molecular evolution rate across birds from @weir2008calibrating, and appear as major outliers compared to alternate estimates for the same nodes based on primary fossil calibrations (Fig. 5).

### 2023-05-30 notes-secondary-calibrations.Rmd
add edits to EJM's edits

Burns et al. 2014: "[we] used a substitution rate of 0.0105 mean substitutions per million years along each branch (Weir and Schluter, 2008)"

>>>>

Burns et al. 2014 used a single secondary calibration point with Bayesian analyses using BEAST v1.7.1: "[we] used a substitution rate of 0.0105 mean substitutions per million years along each branch [from] (Weir and Schluter, 2008)".
